Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Tweaks.

\paragraph{Update the lookup table}
In the beginning, we tried to update the lookup table together with other parameters. But the result was much worse than not updating it. But because deep learning researchers do update the feature learning layers (in our model, just lookup table), it is reasonable to try this. And instead of updating at the beginning of training, we can begin the updating after other parameters are well trained.

@@

\paragraph{Confusion matrices}
We plot the confusion matrix (Figure \ref{Conf_fig}) for the basic RNN model and find that:
\begin{enumerate}
\item The \textbf{most serious confusion is between NNP and NN}. This makes sense because of the fact that the embeddings we are using make no distinction between capitalized and non-capitalized words;
\item  Another strange confusion is from quotes, which was also met in common HMM models. This may come from the overwhelming sequential information, and it makes big difference on accuracy(about 1\% on out-of-domain accuracy), to keep everything trained automatically;
\item Other confusions look normal, and also occur in HMM models, like JJ and NN.
\end{enumerate}
\begin{figure}
\includegraphics[scale=0.5]{indomain_conf.png} 
\includegraphics[scale=0.5]{outdomain_conf.png} 
\caption{Confusion matrices for basic RNN}\label{Conf_fig}
\end{figure}

>>>>

\paragraph{Update the lookup table}
In the beginning, we tried to update the lookup table together with other parameters. But the result was much worse than not updating it. But because deep learning researchers do update the feature learning layers (in our model, just the lookup table), it is reasonable to try this. And instead of updating at the beginning of training, we can begin the updating after other parameters are well trained.

@@

\paragraph{Confusion matrices}
We plot the confusion matrix (Figure \ref{Conf_fig}) for the basic RNN model and find that:
\begin{enumerate}
\item The \textbf{most serious confusion is between NNP and NN}. This makes sense because of the fact that the embeddings we are using make no distinction between capitalized and non-capitalized words;
\item  Another strange confusion is from quotes, which was also met in common HMM models. This may come from the overwhelming sequential information, and it makes a big difference on accuracy (about 1\% on out-of-domain accuracy), to keep everything trained automatically;
\item Other confusions look normal, and also occur in HMM models, like JJ and NN.
\end{enumerate}
\begin{figure}
\includegraphics[scale=0.5]{indomain_conf.png} 
\includegraphics[scale=0.5]{outdomain_conf.png} 
\caption{Confusion matrices for basic RNN}\label{Conf_fig}
\end{figure}
